%-------------------------
    % Resume in Latex
    % Author : Jake Gutierrez
    % Based off of: https://github.com/sb2nov/resume
    % License : MIT
    %------------------------
    
    \documentclass[letterpaper,11pt]{article}
    
    \usepackage{latexsym}
    \usepackage[empty]{fullpage}
    \usepackage{titlesec}
    \usepackage{marvosym}
    \usepackage[usenames,dvipsnames]{color}
    \usepackage{verbatim}
    \usepackage{enumitem}
    \usepackage[hidelinks]{hyperref}
    \usepackage{fancyhdr}
    \usepackage[english]{babel}
    \usepackage{tabularx}
    \input{glyphtounicode}
    
    
    %----------FONT OPTIONS----------
    % sans-serif
    % \usepackage[sfdefault]{FiraSans}
    % \usepackage[sfdefault]{roboto}
    % \usepackage[sfdefault]{noto-sans}
    % \usepackage[default]{sourcesanspro}
    
    % serif
    % \usepackage{CormorantGaramond}
    % \usepackage{charter}
    
    
    \pagestyle{fancy}
    \fancyhf{} % clear all header and footer fields
    \fancyfoot{}
    \renewcommand{\headrulewidth}{0pt}
    \renewcommand{\footrulewidth}{0pt}
    
    % Adjust margins
    \addtolength{\oddsidemargin}{-0.5in}
    \addtolength{\evensidemargin}{-0.5in}
    \addtolength{\textwidth}{1in}
    \addtolength{\topmargin}{-.5in}
    \addtolength{\textheight}{1.0in}
    
    \urlstyle{same}
    
    \raggedbottom
    \raggedright
    \setlength{\tabcolsep}{0in}
    
    % Sections formatting
    \titleformat{\section}{
      \vspace{-4pt}\scshape\raggedright\large
    }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
    
    % Ensure that generate pdf is machine readable/ATS parsable
    \pdfgentounicode=1
    
    %-------------------------
    % Custom commands
    \newcommand{\resumeItem}[1]{
      \item\small{
        {#1 \vspace{-2pt}}
      }
    }
    
    \newcommand{\resumeSubheading}[4]{
      \vspace{-2pt}\item
        \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
          \textbf{#1} & #2 \\
          \textit{\small#3} & \textit{\small #4} \\
        \end{tabular*}\vspace{-7pt}
    }
    
    \newcommand{\resumeSubSubheading}[2]{
        \item
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
          \textit{\small#1} & \textit{\small #2} \\
        \end{tabular*}\vspace{-7pt}
    }
    
    \newcommand{\resumeProjectHeading}[2]{
        \item
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
          \small#1 & #2 \\
        \end{tabular*}\vspace{-7pt}
    }
    
    \newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
    
    \renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
    
    \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
    \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
    \newcommand{\resumeItemListStart}{\begin{itemize}}
    \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
    
    %-------------------------------------------
    %%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    
    \begin{document}
\begin{center}
    \textbf{\Huge \scshape Tanay Yadav}
\end{center}

\begin{center}
\small +91 99264-97633 $|$
\href{mailto:tanayyadav2325@gmail.com}{\underline{tanayyadav2325@gmail.com}} $|$
\href{https://github.com/tanay-codes}{\underline{Github}} $|$
\href{https://leetcode.com/u/cyb3rTanay/}{\underline{LeetCode}} $|$
Jabalpur, MP
\end{center}

%-----------Profile / About Me-----------
\section{Profile}
A motivated engineering student exploring Cyber Security and System-Level Programming. Possessing practical knowledge in Vulnerability Assessment and Penetration Testing (VAPT), Malware Analysis, Cloud Security, and Mobile Application Penetration Testing. Currently learning \textbf{Spring Boot} and its libraries for building scalable \textbf{microservices} and backend applications. Strong in \textbf{Data Structures, Algorithms, and Logic Building} with a focus on problem-solving.

    
    
    %-----------EDUCATION-----------
    \section{Education}
      \resumeSubHeadingListStart
        \resumeSubheading
          {Parul University}{Vadodara, Gujarat}
          {Bachelor of Technology (B.Tech) in Computer Science and Engineering | CGPA: 7.66/10}{August 2023 -- July 2027}
        \resumeSubheading
          {Kendriya Vidyalaya VFJ Shift-I}{Jabalpur, MP}
          {Senior Secondary Education (CBSE), Science Stream | Percentage: 68.8 }{April 2022 -- March 2023}
        \resumeSubheading
          {Kendriya Vidyalaya VFJ Shift-II}{Jabalpur, MP}
          {Secondary Education (CBSE),  | Percentage: 86.0 }{April 2020 -- March 2021}
      \resumeSubHeadingListEnd
    
    
    
    %-----------Extracurriculars-----------

    
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
   {\textbf{Post-Quantum Cryptography Simulator}}{[ \href{https://github.com/raunak-shah666/CpuSchedulerVisualizer}{\underline{GitHub}} ]}
    \resumeItemListStart
         \resumeItem{\textbf{Tools Used:} Kali Linux and Python}
        \resumeItem{Developed a simulator for Post-Quantum Cryptography algorithms such as CRYSTALS-Kyber and CRYSTALS-Dilithium with key generation, encryption/decryption, and digital signature workflows.}
        \resumeItem{Implemented comparative analysis features for classical and post-quantum algorithms based on key size, security level, computation speed, and memory usage.}
        \resumeItem{Designed interactive visualizations to help students and researchers understand quantum-resistant cryptographic mechanisms and algorithm workflows.}
    \resumeItemListEnd
    
\resumeProjectHeading
{\textbf{CPU Scheduler Visualizer}}{[ \href{https://github.com/raunak-shah666/CpuSchedulerVisualizer}{\underline{GitHub}} ]}
\resumeItemListStart
    \resumeItem{\textbf{Tools Used:} HTML, CSS, JavaScript for interactive visualization and \textbf{Java Spring Boot} for backend logic.}
    \resumeItem{Developed a simulator for SJF, FCFS, Round Robin, and Priority Scheduling with process input and Gantt chart generation.}
    \resumeItem{Helps students and educators understand CPU scheduling behavior and analyze system performance visually.}
\resumeItemListEnd


\resumeItemListEnd



\resumeSubHeadingListEnd

   \section{Skills}
\begin{itemize}[leftmargin=0.5cm]
  \item \textbf{Programming Languages:} Java, Python
  \item \textbf{Web Development:} HTML, CSS
  \item \textbf{Databases:} MySQL
  \item \textbf{CS Fundamentals:} Data Structures and Algorithms, Operating Systems, DBMS, Computer Networks
\end{itemize}

    
    

    
    %-----------Courses-----------
    \section{Achievements and Certifications}
    \begin{itemize}[leftmargin=0.5cm]
      \item \textbf{LeetCode} \href{https://leetcode.com/u/cyb3rTanay/}{[Profile]}: 
            Solved \textbf{50+ DSA problems}
      \item \textbf{GeeksforGeeks} \href{https://www.geeksforgeeks.org/profile/cyb3rtanay}{[Profile]}: 
            Solved \textbf{150+ Problems}
            \item \textbf{Quick Heal Certified Cyber Security Analyst} 
            \item \textbf{Quick Heal Certified Malware Analyst and Reverse Engineer} 
      \item \textbf{Quick Heal Certified Vulnerability Assessment and Penetration Testing Analyst} 
    
    \end{document}
